---
title: "Linear model"
author: "Melany Vasquez"
date: "7/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```


## Introduction

Read abut the data from the website and its stage. Then form three regression models: Model 01 is SIMS~ARM, Model 02 is SIMS~GRIP, and Model 03 is SIMS~ARM+GRIP. For each model find a 95%prediction interval of SIMS given a value of 94 for GRIP and 88 for ARM. compare model 01 and model 03 using anova. writ it up in a markdown document, push the project up to your github account and submit on canvas.

You can import data directly from a link to its website. copy and pasting the link to the clipboard by right clicking.


## Methods

This project required a github account repo to be created from scratch. The project needed to be written and the data needed to be read in via SVS file. The helper file needed for this project is Numerical_Numerical. The four variable that are displayed in the environment pane are all numerical variables.

# Results

# Graphical Descriptive results 

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```
  
The y-axis is SIMS and the X-axis is ARM. This plot shows that there is a positive linear correlation.There is a Positive correlation between ARM and SIMS displayed in the plot above.


# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The value is 0.68, which is a positive number that indicates the line will go travel upward towards the right.


# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


The residual standard error represents the standard deviation of the error points 
In this linear regression model, the numbers that should be considered to create the prediction equation are the estimate coefficients. To predict SIMS based on ARM strength, the intercept, -4.1 would be added to .05, ARM and then multiplied by ARM.
This equation for the prediction of SIMS would look like: -4.1 + .05 * ARM.
The formula needed is y=mx + b to create a line. The bigger the adjusted R-squared, the better the model because it means that  of the many erorrs were fixed .The degrees of freedom will be taken away from the Multiple -R squared and then what will be left is the Adjusted R-squared.In the adjusted R square, the error was reduced by 46% (0.467).
The adjusted R-squared represents is the reduction of the error from the mean model on a percentage basis.

The 145 degrees of freedom is how many data points are displayed in the plot. 
The line is to be estimate where it hits the y-axis.Data will change the degree of freedom. Every timeyou add more stuff to the model, the Multiple R-squared will go down a small percentage.



# now add the model (Blue line) fit to our plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

The standard error was 1.226
Each point along the ARM axis, the mean of the distibution is where the line falls. The spread of the dots of the standard deviation of the model distribution. 
Of Each point of the line is a representative of one of the outputs.

Every point displayed in this plot is an error.Take the distance between each point and square it.The sum of all squared errors is the average mean error.Take the value of the average away from every dot, and then add that up.


The equation formula for a line is y=mx+b. This regression line that has been drawn used this formula. The equation for SIMS explained by this line is: SIMS = -4.1 + 0.5 * ARM.

To find the value of SIMS multiply the intercept, -4.095160 and the ARM value, 0.054563.

Multiply 100 by ARM, 0.054563 which equals 5.45. The, add the intercept which is about -4.1.

To figure out what value on the Y-intercept passes over the 100 on the X-axis, refer to the values included. It looks like the value of the Y-intercept would be around 1.25, give or take a few.


```{r}
newdata = data.frame(GRIP=94, ARM = 88)
predict(model.1, newdata, interval = "prediction")
```

This is a prediction interval. How far does one point vary from the 
other 


# Discussion and conclusion 






