---
title: "Linear model"
author: "Melany Vasquez"
date: "7/10/2021"
output: 
  html_document:
    toc: true
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```


## Introduction

Read abut the data from the website and its stage. Then form three regression models: Model 01 is SIMS~ARM, Model 02 is SIMS~GRIP, and Model 03 is SIMS~ARM+GRIP. For each model find a 95%prediction interval of SIMS given a value of 94 for GRIP and 88 for ARM. compare model 01 and model 03 using anova. write it up in a markdown document, push the project up to your github account and submit on canvas.

You can import data directly from a link to its website. copy and pasting the link to the clipboard by right clicking.


# SIMS~ARM








plot scatterplot 


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
#### Basic scatterplot

```{r}
basicNN + geom_point()
```
  
The y-axis is SIMS and the X-axis is ARM. This plot shows that there is a positive linear correlation.There is a Positive correlation between ARM and SIMS displayed in the plot above.


#### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The value is 0.68, which is a positive number that indicates the line will go travel upward towards the right.


#### Inferential Results
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

This model is better than the one for GRIP. The Adjusted R-squaredis bigger, which means more errors were made.

If you go 1.22 up or down that is the prediction interval

The residual standard error represents the standard deviation of the error points 
In this linear regression model, the numbers that should be considered to create the prediction equation are the estimate coefficients. To predict SIMS based on ARM strength, the intercept, -4.1 would be added to .05, ARM and then multiplied by ARM.
This equation for the prediction of SIMS would look like: -4.1 + .05 * ARM.
The formula needed is y=mx + b to create a line. The bigger the adjusted R-squared, the better the model because it means that  of the many erorrs were fixed .The degrees of freedom will be taken away from the Multiple -R squared and then what will be left is the Adjusted R-squared.In the adjusted R square, the error was reduced by 46% (0.467).
The adjusted R-squared represents is the reduction of the error from the mean model on a percentage basis.

The 145 degrees of freedom is how many data points are displayed in the plot. 
The line is to be estimate where it hits the y-axis.Data will change the degree of freedom. Every timeyou add more stuff to the model, the Multiple R-squared will go down a small percentage.



#### the model (Blue line)
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

The standard error was 1.226
Each point along the ARM axis, the mean of the distibution is where the line falls. The spread of the dots of the standard deviation of the model distribution. 
Of Each point of the line is a representative of one of the outputs.

Every point displayed in this plot is an error.Take the distance between each point and square it.The sum of all squared errors is the average mean error.Take the value of the average away from every dot, and then add that up.


The equation formula for a line is y=mx+b. This regression line that has been drawn used this formula. The equation for SIMS explained by this line is: SIMS = -4.1 + 0.5 * ARM.

To find the value of SIMS multiply the intercept, -4.095160 and the ARM value, 0.054563.

Multiply 100 by ARM, 0.054563 which equals 5.45. The, add the intercept which is about -4.1.

To figure out what value on the Y-intercept passes over the 100 on the X-axis, refer to the values included. It looks like the value of the Y-intercept would be around 1.25, give or take a few.


```{r}
newdata = data.frame(GRIP=94, ARM = 88)
predict(model.1, newdata, interval = "prediction")
```

This is a prediction interval. How far does one point vary from the other.If you take .7 away from 3.13, you would end up approximately 2.3.
The model predictedd a SIMS score of .706, where the 95% confidence interval -1.726 to 3.139









# SIMS~GRIP



plot scatterplot 

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```
#### Basic scatterplot

```{r}
basicNN + geom_point()
```

The points in this plot are more closely knit.



#### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation is 0.63. The number of the correlation , the closer the point are to eachotjer. This correlation is a bit smaller than the previous correlation in model 01 between the ARM.

#### Inferential Results
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The adjusted R-square is 0.4053.previously, the number was 0.409
The small standard error makes for a successful model.This model is not as good as the model 01 with ARM because the standard deviation is larger.Notice the difference between the multiple R-squared and the adjusted R-squared.



#### the model (Blue line) 
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 
Again every dot or point displayed in this plot is an error.Take the distance between each point and square it.The sum of all squared errors is the average mean error.Take the value of the average away from every dot, and then add that up.
The equation formula for a line is y=mx+b. This regression line that has been drawn used this formula. The equation for SIMS explained by this line is: SIMS = -3.10 + 2.0 * GRIP

To figure out what value on the Y-intercept passes over the 100 on the X-axis, refer to the values included. It looks like the value of the Y-intercept would be around 1.25, give or take a few.


```{r}
predict(model.2, newdata, interval = "prediction")
predict(model.2, newdata, interval = "confidence")
```


The first line is the prediction interval, the second line is the confidence interval. 
The prediction interval is predicting where the next point will be placed.
The confidence interval is a prediction of where the line will be place, in range from -8 to -0.27

The uper and lower predictions represent the threshhold.
The prediction interval says that were 95% confident that the prediction using this model is within these bounds.



# SIMS~ARM + GRIP


### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```



#### Inferential Results
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

GRIP * .024470 + ARM * .037 = SIMS 

The residual standard error is the variation in all points.
The bigger the Adjusted R square the better the model.The multiple R-squarews is always a little bit bigger than the adjusted R-square.The bigger the adjusted R square the more you reduce the error.





```{r}
predict(model.3, newdata, interval = "prediction")
```


### Inferential (Build 2-dimensional model.3)





```{r}
model.3 <- lm(SIMS~GRIP + ARM ,data=data)
summary.lm(model.3)
```



#### predict model.3 at target point

```{r}
predict(model.3, newdata, interval = "prediction")
```


## comparing nested models ANOVA test

### Model.01 vs Model,03

Model 1 and Model 3 are nested

```{r}
anova(model.1,model.3)
```

The p-value is 0.00000499. The results are unlikely to occur by chance.
null hypothesis is rejected in favor of the alternative.
The residual degree of freedom is 145. All the errors together add up to 217.The errors were reduced by 29.45.

### Model.2 vs. Model 03

```{r}
anova(model.2,model.3)
```

The p-value is based on on the results of 0.000000001495. These results are unliekly to occur by chance. 

Model 2 is nested in model 3. The components in model 2 are in 3.

## Informally compare Model.1 with Model.2


```{r}
anova(model.1,model.2)
```

0.467 is the adjusted R-squared for SIMS~ARM

0.4053 is the adjusted R-squared fro SIMS~GRIP
  
How much the models are able to guess the average.

# Model comparisson


The models must be nested. That means all the independent variable in one model are also included in all the other models. SIMS is a function of ARM. Model 2 is nested in model 03, and Model 01 in model 03. model 01 and 02 are nested into model 03 and models 01 and 02 are not.


## Asessing SIM~ARM (how good it is)

According to inferential results declared in each model (Model 01,Model 02, and Model p3. The adjusted R-square is what 
tells me and lets me know which models are the ones that work best. SIM~ARM which was Model 01, accordingly the degrees of
freedom taken away from the Multiple -R squared and then what was left is the Adjusted R-squared. In the adjusted R 
square, the error was reduced by 46% (0.467).he adjusted R-squared represents is the reduction of the error from the mean 
model on a percentage basis. Meaning There was not much in this model (01) to see, there was a positive outcome like the 
rest however,it was still not the best out of all three models as many errors there were.  



### Comparing SIMS~ARM to SIM~GRIP

The main idea here is to tell which of the three models is the best sculpted and the highest number each gets inferantially in the R-square the better it is placed.

SIMS~ARM like previously stated, it did have many errors and it was positively running in the R-square. However, they are not compatible against each other. For starters they have no similar components and the r-square in the inferential results implied that model 02, which is SIMS~GRIP is way better made with mistakes rather than model 01 which is SIMS~ARM.


### Comparing SIMS~ARM to SIMS~ARM+GRIP 

SIMS~ARM was trash compared to SIMS~ARM +GRIP. SIMS~ARM+GRIP was the best model with the R-square of 0.5, meaning there were all the more errors. But overall model 01 (SIMS~ARM) is able to nest into Model 03 (SIMS~ARM+GRIP). Model 03 had a the requirements and the highest number and amounts of errors that model 01 ( SIMS~ARM) did not have and only had about 0.467 which was not much maybe 40% and Model 03 had 2xs as much. And what we wanted for results was MORE errors so that there would be a more perfect design in the models showed above.

#### Statistical test of SIMS~ARM | SIMS~ARM+GRIP


SIMS~ARM and SIMS~ARM+GRIP were not identical at all. Therefore. The best model is model 03 SIMS~ ARM+GRIP, that being because the adjusted R-square was at .53. thi means that the most errors were removed on here ratherin the other two models the models were all about .4.
The second best model was model 02 SIMS~GRIP , becasue its adjusted R-square landed around .4053, it was closest to the .5/model 03 and 40% of the errors that were made were reduced. 
The most useless model of all three was Model 01, SIMS~ARM although it can synch/ "nest" into model 03. It had awfully many error and was also the least effective to create less errors. The adjusted R-square of this model was only .467, which was a fail.


One thing that we can confirm though is the fact that Models 01 and 02 can nest or fixate into model 03 pretty well since  models have components that match model 03.
however models 01 and 02 cannot nest together. 


